\textbf{NBA Party}

### 2017-07-03 init_model.rnw
Mainly formatting changes to plots, and stargazer tables.

load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/population_by_county_year.RData')
load(file = 'tmp_data/studios_and_artists_nba.RData')

musicians <- copy(dt)
rm(dt)
setnames(musicians, 'variable', 'nmusicians')
musicians <- merge(musicians, pop, by = c('county', 'season'), all.x = T)

@@

<<echo=F,results='hide'>>=
musicians[, county := gsub(' (county)|(division),.*$', '', county, ignore.case = T)]
@

@@

setkey(nba.lines, season, team, date)

### Exclude playoff games.
nba.lines <- nba.lines[, head(.SD, n=82), by=list(season,team)]

@@

<<echo=F>>= 
musicians[, list(average.nmusicians = mean(nmusicians) %>% round(., digits = 1)),
          by = team][order(average.nmusicians)][c(1:5, 25:29)]
@

@@

pdf('writing/Party_by_Team_Location.pdf', width = 14, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$party.continuous, 
     main = 'Continuous measure of party by Team Location: NBA',
     ylab = 'Log Avg of Musicians and Sound Recording Studios',
     xlab = '',
     axes = F)
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
## text(x = ticks, y = 1.25, labels = tmp$team, srt = 90)
axis(side = 2)
dev.off()

@@

@@

tmpm <- nba.lines[, list(log.nmusicians = mean(log(nmusicians+1), na.rm = T),
                         log.population = mean(log(population),   na.rm = T)), 
                  by = team][order(log.nmusicians)] %>% na.omit
tmpd <- drinking[, list(log.ndrinks = mean(log(ndrinks+1))), 
                  by = team][order(log.ndrinks)] %>% na.omit
tmp <- merge(tmpm, tmpd, by = 'team')
setorder(tmp, log.nmusicians)

pdf('writing/why_drinks_or_population_dont_work.pdf', width = 16, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$log.nmusicians,
     main = 'Why drinking establishments or population don\'t work as a proxy for nightlife',
     ylab = 'Log Avg of Variable',
     xlab = '', axes = F, pch = 1, ylim = c(0, max(tmp$log.population)))
points(x = ticks, y = tmp$log.ndrinks, pch = 16, col = 'purple')
points(x = ticks, y = tmp$log.population, pch = 18, col = 'orange')
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
legend(x = 21.5, y = 12.5, legend = c('Musicians and sound recording studios',
                                 'Drinking establishments and liquor stores',
                                 'Population'), pch = c(1, 16, 18), col = c('black', 'purple', 'orange'))
text(x = 24.6, y = 9.5, labels = paste("Correlation (alcohol):       ", 
                                       cor(tmp$log.nmusicians, tmp$log.ndrinks) %>% round(., 3)))
text(x = 24.6, y = 10, labels = paste("Correlation (population): ", 
                                       cor(tmp$log.nmusicians, tmp$log.population) %>% round(., 3)))
dev.off()

@@

m3 <- glm(I(team.score > opponent.score) ~ party + odds + I(team == location) + 
             ndays.lgame + log(travel.dist+1) + weekend,
         data = mlb.lines, family = 'binomial')
summary(m3)
m4 <- update(m3, . ~ party.now + . - party)

@@

stargazer(m4, covariate.labels = c('Party placebo',
                                   'Bookmaker\'s odds', 'Home-team effect',
                                   'Number of rest days', 'Logged travel distance',
                                   'Weekend', 'Constant'), 
          dep.var.labels = 'Probability of Winning (MLB)')

@@

pdf('writing/Party_by_Team_Location_mlb.pdf', width = 14, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$party.continuous, 
     main = 'Continuous measure of party by Team Location: MLB',
     ylab = 'Log Avg of Musicians and Sound Recording Studios',
     xlab = '',
     axes = F)
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
dev.off()

>>>>

load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/population_by_MSA_year.RData')
load(file = 'tmp_data/studios_and_artists_nba.RData')

musicians <- copy(dt)
rm(dt)
setnames(musicians, 'variable', 'nmusicians')

### This is simply ad-hoc.
musicians[, population := 0.0]
for (i in 1:nrow(musicians))
    set(musicians, i, j = 'population', 
        value = pop[grepl(musicians[i, locality], locality) &
                    grepl(musicians[i, state],    locality) &
                    musicians[i, season] == season, mean(population)])

@@

<<echo=F,results='hide'>>=
#musicians[, county := gsub(' (county)|(division),.*$', '', county, ignore.case = T)]
@

@@

### Exclude playoff games.
setkey(nba.lines, season, team, date)
nba.lines <- nba.lines[, head(.SD, n=82), by=list(season,team)]

@@

<<echo=F>>= 
musicians[, list(average.nmusicians = mean(nmusicians) %>% round(., digits = 1)),
          by = team][order(average.nmusicians)][c(1:5, 25:27)]
@

@@

pdf('writing/Party_by_Team_Location.pdf', width = 14, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$party.continuous, 
     main = 'Continuous measure of party by Team Location: NBA',
     ylab = 'Log sum of Musicians and Sound Recording Studios',
     xlab = '',
     axes = F)
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
## text(x = ticks, y = 1.25, labels = tmp$team, srt = 90)
axis(side = 2)
dev.off()

@@

pdf('writing/next_day_opponent_on_tour.pdf', width = 14, height = 14)
ggplot(tmp[cur.game == 'Current game away' &
           lst.game == 'Last game away'], aes(x = location, y = last.game.loc, fill = log(N))) +
    geom_tile() +
    labs(x = 'Current Game Location', y = 'Last Game Location', 
         title = 'Distribution of Next Day Opponent - NBA\n(sorted by distance to NYC)') +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 315, vjust = 0.5),
          plot.title = element_text(hjust=.5))
dev.off()

@@

tmpm <- nba.lines[, list(log.nmusicians = mean(log(nmusicians+1), na.rm = T),
                         log.population = mean(log(population+1), na.rm = T)), 
                  by = team][order(log.nmusicians)] %>% na.omit
tmpd <- drinking[, list(log.ndrinks = mean(log(ndrinks+1))), 
                  by = team][order(log.ndrinks)] %>% na.omit
tmp <- merge(tmpm, tmpd, by = 'team')
setorder(tmp, log.nmusicians)

pdf('writing/why_drinks_or_population_dont_work.pdf', width = 16, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$log.nmusicians,
     main = 'Why drinking establishments or population don\'t work as a proxy for nightlife',
     ylab = 'Log sum of Variable',
     xlab = '', axes = F, pch = 1, ylim = c(0, max(tmp$log.population)), type = 'l')
points(x = ticks, y = tmp$log.ndrinks, pch = 16, col = 'purple', type = 'l')
points(x = ticks, y = tmp$log.population, pch = 18, col = 'orange', type = 'l')
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
legend(x = 1.5, y = 12.5, legend = c('Musicians and sound recording studios',
                                 'Drinking establishments and liquor stores',
                                 'Population'), pch = c(1, 16, 18), col = c('black', 'purple', 'orange'))
text(x = 3.6, y = 9.5, labels = paste("Correlation (alcohol):       ", 
                                       cor(tmp$log.nmusicians, tmp$log.ndrinks) %>% round(., 3)))
text(x = 3.6, y = 10, labels = paste("Correlation (population): ", 
                                       cor(tmp$log.nmusicians, tmp$log.population) %>% round(., 3)))
dev.off()

@@

m3 <- glm(I(team.score > opponent.score) ~ party + odds + I(team == location) + 
             ndays.lgame + log(travel.dist+1) + weekend,
         data = mlb.lines[season < 2017], family = 'binomial')
summary(m3)
m4 <- update(m3, . ~ party.now + . - party)

@@

@@

pdf('writing/Party_by_Team_Location_mlb.pdf', width = 14, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$party.continuous, 
     main = 'Continuous measure of party by Team Location: MLB',
     ylab = 'Log sum of Musicians and Sound Recording Studios',
     xlab = '',
     axes = F)
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
dev.off()
